Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.6)} \underline{Drafting Committee: DC90 (\today)}

### 2011-02-11 results.tex
Changed a typo

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish at \blue{small} $-t$ values due to the dependence of the amplitude on the factor $k$ from in Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitudes are compatible with zero, as are the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes\blue{, which are} dependent on the squared DVCS term. These \blue{$A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes} are shown in the second row of Fig.~\ref{bsa_xbjrange}. Neither the \blue{$A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitudes} show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands of the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used \blue{used in the various stages} of the H{\sc ermes} experiment.

>>>>

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish at \blue{small} $-t$ values due to the dependence of the amplitude on the factor $k$ from in Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitudes are compatible with zero, as are the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes\blue{, which are} dependent on the squared DVCS term. These \blue{$A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes} are shown in the second row of Fig.~\ref{bsa_xbjrange}. Neither the \blue{$A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitudes} show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands of the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment \blue{used in the various stages} of the H{\sc ermes} experiment.
